---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# uncorbets

<!-- badges: start -->

[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental) [![Codecov test coverage](https://codecov.io/gh/Reckziegel/uncorbets/branch/main/graph/badge.svg)](https://codecov.io/gh/Reckziegel/uncorbets?branch=main) [![R-CMD-check](https://github.com/Reckziegel/uncorbets/workflows/R-CMD-check/badge.svg)](https://github.com/Reckziegel/uncorbets/actions)

<!-- badges: end -->

The Euler theorem has been widely used in finance as a way to decompose homogeneous risk measures of degree one. Unfortunately, this decomposition does not isolate the true sources of risk.

The Minimum Torsion Bets (MTB) offers a solution to this problem: it uses the spectral decomposition to "pick" the uncorrelated factors that are as close as possible to the original variables, among all living matrix rotations.

The output is a diversification distribution with the following properties: it's always positive, sums to $1$, capture the true sources risk and have an insightful interpretation. The above characteristics put the Effective Number of Minimum Torsion Bets as a generalization of the Marginal Contribution to Risk (MCR).

## Example

```{r}
library(uncorbets)

# prepare data
returns <- diff(log(EuStockMarkets))
covariance <- cov(returns)

# Minimum Torsion Matrix
torsion_mat <- torsion(covariance)

# Prior Allocation (equal weights, for example)
w <- rep(1 / ncol(returns), ncol(returns))

# Compute diversification distribution and the diversification level
effective_bets(b = w, sigma = covariance, t = torsion_mat)

# maximize the effective number of bets (enb)
max_effective_bets(x0 = w, sigma = covariance, t = torsion_mat)
```

## Installation

Install the released version from CRAN with:

``` r
install.packages("uncorbets")
```

Install the development version of `uncorbets` from github with:

``` r
# install.packages("devtools")
devtools::install_github("Reckziegel/uncorbets")
```

## References

-   Meucci, Attilio and Santangelo, Alberto and Deguest, Romain, Risk Budgeting and Diversification Based on Optimized Uncorrelated Factors (November 10, 2015). Available at SSRN: <https://www.ssrn.com/abstract=2276632> or <http://dx.doi.org/10.2139/ssrn.2276632>

-   Attilio Meucci (2021). Portfolio Diversification Based on Optimized Uncorrelated Factors (<https://www.mathworks.com/matlabcentral/fileexchange/43245-portfolio-diversi-cation-based-on-optimized-uncorrelated-factors>), MATLAB Central File Exchange. Retrieved July 8, 2021.
